%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
    {
        Software Engineer $~\mid~$
        Distributed Systems, High Load,
        Linux, C++, Python
    } % Job title
    {Yandex} % Organization
    {Saint-Petersburg, Russia} % Location
    {Jan 2024 - Now} % Date(s)
    {
        \begin{cvitems}
          \item {
              Participated in development and support of a core infrastructure pub/sub service
              (\approx 20 million RPS).
          }
          \item {
              Developed an SNS compatible API as a part of public service API. Ensured compatibility
              with existing SDKs.
          }
          \item {
              Designed and implemented SMS and WebPush notification channels support with SNS-compatible API.
          }
          \item {
              Conducted a resource consumption review and performed a horizontal scaling of the main
              stateful component.
          }
          \item {
              Drove \underline{\href{https://www.boost.org/doc/libs/1_87_0/doc/html/boost_asio.html}{Boost.Asio}}
              upgrade (from 1.74 to 1.86), which required rewriting a lot of low-level ASIO code
              repository-wise.
          }
          \item {
              Set up code linting and formatting CI checks to ensure high code quality.
              Helped my team to set up LSP in their coding environment.
          }
        \end{cvitems}
    }

    \cventry
    {
        Senior Software Engineer $~\mid~$
        Embedded Systems, Storage Systems,
        Linux, C++, C, Python
    } % Job title
    {YADRO} % Organization
    {Saint-Petersburg, Russia} % Location
    {May 2023 - Jan 2024} % Date(s)
    {
        \begin{cvitems}
          \item {
            Implemented and deployed a write-ahead log used for crash and transaction
            recovery in partial failure mode.
          }
        \end{cvitems}
    }

    \cventry
    {
        Software Engineer $~\mid~$
        Distributed Systems, High Load
        Linux, C++, CUDA, Python,
        Inference, gRPC
    } % Job title
    {Yandex SDG} % Organization
    {Saint-Petersburg, Russia} % Location
    {Oct 2021 - May 2023} % Date(s)
    {
        \begin{cvitems}
        \item {
          Designed and implemented a remote inference service.
          Much like \underline{\href{https://github.com/triton-inference-server/server}{Triton}}
          but tailored exactly to our needs and technologies.
        }
        \item {
          Increased mean GPU utilization by 6 times when compared to a separate
          GPU per operation and by 4 times when compared to Triton.
        }
        \item {
          This led to large savings in operational costs and helped developers verify and deploy their ideas faster.
        }
        \item {
          Implemented a cluster autoscaler paired with service discovery
          service suitable for multi-tenant and QoS-critical scenarios.
        }
        \item {
          Ensured observability and debuggability of the service by ensuring
          that monitorings, logs and alerts are in place and well-documented.
        }
        \end{cvitems}
    }

  %\cventry
    %{
        %Software Engineer $~\mid~$
        %Research, HPC, Inference,
        %C++, Python, Inference, ML/MLOps
    %} % Job title
    %{Huawei \& ITMO university} % Organization
    %{Saint-Petersburg, Russia} % Location
    %{May 2021 - Sept 2021} % Date(s)
    %{
      %\begin{cvitems}
        %\item {
            %Developed fast, small and concise C/C++ implementations of specific RNN ML algorithms.
        %}
        %\item {
            %Built a compression tool on top of the models' implementations.
        %}
        %\item {
            %The solution proved to be \underline{a highly competitive compression tool}
            %in terms of both CR and resource consumption.
        %}
      %\end{cvitems}
    %}


  %\cventry
    %{
        %Software Engineer $~\mid~$
        %Research, HPC, C, Python,
        %Background Modelling,
        %Compression, HEVC
    %} % Job title
    %{Huawei \& ITMO university} % Organization
    %{Saint-Petersburg, Russia} % Location
    %{Oct 2020 - Apr 2021} % Date(s)
    %{
      %\begin{cvitems} % Description(s) of tasks/responsibilities
        %\item {
            %Developed low latency and high throughput background extraction algorithms.
        %}
        %\item {
            %Created a set of metrics to fine tune and compare these algorithms.
        %}
        %\item {
            %Integrated the algorithms into HEVC and x265 encoders. The resulting encoder
            %\underline{shows considerable growth in CR} while slightly compromising performance when
            %compared to the original encoder.
        %}
      %\end{cvitems}
    %}

\end{cventries}
